---
title: "R Notebook"
output: html_notebook
---
#### Importing Data Science Package via Tidyverse
```{r}
#Imports Packages such as; ggplot2,dplyr,tidyr,readr,purrr,tibble,stringr and,forcats
# with a single line call

library(tidyverse)

```



#### 1. Write a multiplication script using either a “for” loop or a “while” loop. Show your script.
(5 points)

```{r}
for (i in 0:5) {
  print(i*2)
}
```

#### 2. Using the customers data (custdata.tsv). Like histogram, you can also plot the density of a variable.
```{r}
customerFP = 'Data/custdata.tsv'
customerDF = read.table(file = customerFP, sep = '\t', header = TRUE)
```

#### 2.1: Figure out how to plot density of income. ​(5 points)
```{r}
ggplot(customerDF, aes(x=income)) + geom_density()
```

#### 2.2: Provide a couple of sentences of description along with the plot. Imagine you are explaining this to your manager or a senior leader. ​(5 points)

```{r}

```

#### 3.1: Create a bar chart for housing type using the customers data. Make sure to remove the “NA” type. [Hint: You can use subset function with an appropriate condition on housing type field.] Provide your commands and the plot.(5 points)

```{r}
subsetHousingType = customerDF[complete.cases(customerDF[ , 7]),]

ggplot(subsetHousingType) + geom_bar(aes(x=housing.type))

```

#### 4.1: Extract a subset of customers that are married and have an income more than $50,000. ​(5 points)
```{r}
marriedByIncome = subset(customerDF, marital.stat == "Married" & income > 50000)
marriedByIncome
```

#### 4.2: What percentage of these customers have health insurance? ​(5 points)
```{r}

marriedByIncome %>%
  group_by(health.ins) %>%
  summarise(percent = round(100 * n()/nrow(marriedByIncome),digits = 2))

```

#### 4.3: How does this percentage differ from that for the whole data set? ​(5 points)
```{r}

```

#### 5.1: In the customers data, do you think there is any correlation between age,income, and number of vehicles? Explain why or why not. ​(5 points)
```{r}

```

#### 5.2: Report your correlation numbers and interpretations. [Hint: Make sure to remove invalid data points, otherwise you may get incorrect answers!] ​(10 points)
```{r}

```

#### 6. You are given a data file containing observations for dating. Someone who dated 1000 people (!) recorded data about how much that person travels (Miles), plays games (Games, and eats ice cream (Icecream). With this, the decision about that person (Like) is also noted. Use this data to answer the following questions using R:

#### 6.1: Is there a relationship between eating ice cream and playing games? What about traveling and playing games? Report correlation values for these and comment on them. ​(10 points)
```{r}

```


#### 6.2: Let us use Miles to predict Games. Perform regression using Miles as the predictor and Games as the response variable. Show the regression graph with the regression line. Write the line equation. ​(10 points)
```{r}

```

#### 6.3: Now let us see how well we can cluster the data based on the outcome (Like). Use Miles and Games to plot the data and color the points using Like. Now cluster the data using k-means and plot the same data using clustering information. Show the plot and compare it with the previous plot. Provide your thoughts about how well your clustering worked in two to four sentences. ​(10 points)
```{r}

```
